\chapter{Components}
	\begin{itemize}
		\item this rulebook
		\item 1 game board
		\item 2 wooden Round markers
		\item 1 six-sided die
		\item n wooden Player markers %max num players * 3	
		\item m cards %max num players * 7
		\item o round cardboard tokens representing ``Coins''
		\item p wooden green cubes representing ``SPINach''
		\item q hexagonal cardboard tokens representing ``Victory Points''
	\end{itemize}
	\section{Component Overview}
This section provides a brief overview of every game component.
		\subsection{Game Board}
The game board depicts the eight Seasons of a year upon a Big Top, contains tracks for displaying players' statistics and also provides all of the information required to play the game.
		\subsection{Round Markers}
Round markers are used to indicate the game's current Season and Year.
		\subsection{Player Markers}
Player markers are used to indicate each players' current statistics for Notoriety, owned Prop and Skill level which increase as the different actions are played.
		\subsection{Action Cards}
Each player selects an action to do each round. 
This is done secretly since several of the actions may cause interactions with other players, depending upon what they choose.
		\subsection{Coins}
Coins are the main currency of the game which can be used to purchase better props and admittance to Festivals.
Trading between players is also possible.
		\subsection{SPINach}
The plant which magically boosts your Skill level when had at Festivals.
Again, this can be traded amongst players.
		\subsection{Victory Points}
These are the prizes players obtain for performing in Shows held at the end of Festivals.
Whichever player end up with the most takes ultimate victory!
